### 2019-10-08 thesis/txt/0-introduction.tex
literature research about CI and benefits

\chapter{Introduction}
\plan{motivate why information extraction from build logs}
Many software projects now use continious integration (CI) to improve \mention{reasons to do this, look into Proksch papers}. These CI builds often produce very long and verbose build logs \mention{add log characteristics, cite what Moritz cited in his proposal?}, stating the progress and results of the various steps within the build.

>>>>

\chapter{Introduction}
\plan{motivate why information extraction from build logs}
Many software projects now use continuous integration (CI)~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs more easily~\cite{vasilescu2015quality,duvall2007continuous} and improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}. These CI builds often produce very long and verbose build logs \mention{add log characteristics, cite what Moritz cited in his proposal?}, stating the progress and results of the various steps within the build.
